---
title: "Basics of Quarto documentation"
author: "Usman Afzali"
date: "2024-07-18"
categories: [quarto, documentation]
output: 
  html_document: 
    theme: cerulean
    highlight: espresso
    toc: yes
    number_sections: yes
bibliography: references.bib
---

# Heading 1

## Heading 2

### Heading 3

#### Heading 4

##### Heading 5

###### Heading 6

*Italic*

**Bold**

***Bold Italic***

### Listing items

1.  List item 1
2.  List item 2

### Bullet points

-   bullet 1
-   bullet 2

#### Inserting a hyperlink

Link: [My website](https://www.usmanafzali.com)

### Embed R code

```{r}
#| echo: false
#| include: false
college <- readr::read_csv('http://672258.youcanlearnit.net/college.csv')
```

```{r}
#| echo: false
#| include: false
summary(college)
```

Set some variables as factors.

```{r}
#| echo: false
#| include: false
library(dplyr)
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree), control=as.factor(control),
         gender=as.factor(gender))
```

see summary again

```{r}
#| echo: false
#| include: false
summary(college)
```

default loan rate looks problematic. let's find out

```{r}
#| echo: false
#| include: false
unique(college$loan_default_rate)
```

there is a null and we need to get rid of it

```{r}
#| echo: false
#| include: false
college <- college %>%
  mutate(loan_default_rate=as.numeric(loan_default_rate))
```

summary again

```{r}
#| echo: false
#| include: false
summary(college)
```

looks ok now. there seem to be 2 NA values.

basic plot

```{r}
#| echo: false
#| include: false
library(ggplot2)
ggplot(data=college) + 
  geom_point(mapping = aes(x=tuition, y = sat_avg))
```

there is no much diff. so let's colour instead of shape.

```{r}
#| echo: false
#| include: false
ggplot(data=college) + 
  geom_point(mapping = aes(x=tuition, y = sat_avg, color = control))
```

Association between SAT score and tuition fee in the US colleges, factored by institution type and number of students.

```{r}
#| echo: false
ggplot(data=college) + 
  geom_point(mapping = aes(x=tuition, y = sat_avg, color = control, size = undergrads), 
             alpha=1/2) +
  annotate("text", label="Elite Privates", x=45000, y=1400) +
  geom_hline(yintercept=mean(college$sat_avg)) +
  annotate("text", label="Mean SAT", x=47500, y=mean(college$sat_avg)-15) +
  geom_vline(xintercept = mean(college$tuition)) +
  annotate("text", label="Mean Tuition", y=700, x=mean(college$tuition)+7500) +
  theme(panel.background = element_blank(), legend.key = element_blank()) +
  scale_color_discrete(name="Institution Type") +
  scale_size_continuous(name="Undergraduates") +
  scale_x_continuous(name="Tuition") +
  scale_y_continuous(name="SAT score")
```

According to @morton2024 and @ploeg2024

As @morton2024 said...
